Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex
nudge

\note{
Note that, while we have several reference to the appendix throughout
the paper, the paper can be read on its own and these references are
only meant as an aid for the reader less familiar with control theory or
for the proofs of theorems.
}

@@

Since we are interested in synthesising controllers with observers, 
in this section we will look at checking stability, safety and the response time in the presence of an observer.\footnote{A full description of
the theory related to observer design is in Appendix \ref{sec:control_theory}.}

>>>>

%\note{
%Note that, while we have several reference to the appendix throughout
%the paper, the paper can be read on its own and these references are
%only meant as an aid for the reader less familiar with control theory or
%for the proofs of theorems.
%}

@@

Since we are interested in synthesising controllers with observers, 
in this section we will look at checking stability, safety and the response time in the presence of an observer.
%\footnote{A full description of the theory related to observer design is in Appendix \ref{sec:control_theory}.}
